\begin{song}
\songtitle{Berkeley California}
\firstline{In a dark dim machine room}

\begin{songmeta}
Melodi: Hotel California
Text: David Barr, Ken Hornstein, Greg Nagy
Musik: Don Felder, Glenn Frey, Don Henley
\end{songmeta}

\begin{songtext}
In a dark dim machine room,
cool A/C in my hair,
warm smell of silicon
rising up through the air.
Up ahead in the distance,
I saw a Solarian(tm) light.
My kernel grew heavy, and my disk grew slim.
I had to halt(8) for the night.
The backup spun in the tape drive.
I heard a terminal bell.
And I was thinking to myself:
This could be BSD or USL.
Then they started a lawsuit
and they showed me the way.
There were salesmen down the corridor.
I thought I heard them say:

Welcome to Berkeley California.
Such a lovely place, (Such a lovely place)
Such a lovely trace(1)
Plenty of jobs at Berkeley California.
Any time of year, (Any time of year)
you can find one here.
You can find one here.

Their code was definitely twisted,
but they've got the stock market trends.
They've got a lot of pretty, pretty lawyers
that they call friends.
How they dance in the courtroom,
see BSDI sweat.
Some sue to remember,
some sue to forget.
So I called up Kernighan:
Please bring me ctime(3)
He said:
We haven't had that tm_year since 1969.
And still those functions are calling from far away.
Wake up Jobs in the middle of the night,
just to hear them say:

Welcome to Berkeley California.
Such a lovely Place,
(Such a lovely Place)
such a lovely trace(1)
They're livin' it up suing Berkeley California.
What a nice surprise,
(What a nice surprise)
bring your alibies.

\newpage
Windows NT a dreaming,
Pink OS on ice.
And they said:
We are all just prisoners here
of a marketing device.
And in the judges' chambers
they gathered for the feast.
They diff(1)'d the source code listings
but they can't kill -9 the beast.
Last thing I remember,
I was restore(8)'ing | more(1)
I had to find the soft link back
to the path I was before.
sleep(3) said the pagedaemon
We are programmed to recv(2)
You can swap out any time you like
But you can never leave(1)
\end{songtext}

\begin{songnotes}
[substitute whirring of disk and tape drives for guitar solo]
Skriven av David Barr, Ken Hornstein och Greg Nagy i ljuset av stämningsmålet
mellan AT\&T och BSDI (1992) samt att Sun m.fl. bytte ut gamla go'a BSD mot System V.
\end{songnotes}
\end{song}
